Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-08-08 Reply_Referee1.tex

\author{Ot\'avio Bartalotti \and Gray Calhoun \and Yang He\thanks{%
  All authors: Department of Economics, Iowa State University.
  260 Heady Hall, Ames, IA 50011.
  Bartalotti: \protect\url{bartalot@iastate.edu};
  Calhoun: \protect\url{gcalhoun@iastate.edu} and
  \protect\url{http://gray.clhn.org};
  He: \protect\url{yanghe@iastate.edu}.}}

\begin{document}
\maketitle

First, we thank the reviewer for providing detailed and helpful comments, which we feel have significantly improved the quality of the draft.  Below we provide replies to the reviewer’s specific comments detailing how we address each comment.

\section{General overview of changes}

For this version of the paper, we have changed the bootstrap method from the
residual bootstrap to the wild bootstrap. We have also updated the simulations
to include DGPs featuring heteroskedasticity. We believe that the residual
bootstrap used in the previous version is theoretically correct even under
heteroskedastcity as long as the conditional variance is assumed to be smooth in
a neighorbood around the cutoff point, since the residual bootstrap we initially
proposed only resampled from that neighborhood, but we agree that in practice
the wild bootstrap is likely to be more accurate and can accomodate forms of
conditional heteroskedasticity that the residual bootstrap can not.

We have also relaxed the ``uniform kernel'' requirement and allow other kernels
that are popular in practice. The title of the paper has been updated to reflect
that change.

The first referee expressed concern about the possible computational complexity of
using an iterated bootstrap to produce confidence intervals. This is much less
of an issue than it appears, because many of the matrix calculations can be
computed once and then reused in the bootstrap replications. (Any calculation
that does not involve $Y$ can be reused.) Each bootstrap replication only
requires a small number of matrix-vector multiplications which can be completed
very quickly. We have added a short section after Algorithm 2 that explains
this implementation detail, and we have also provided open source R code that
implements the procedure efficiently.

### 2016-08-08 Reply_Referee2.tex

\author{Ot\'avio Bartalotti \and Gray Calhoun \and Yang He\thanks{%
  All authors: Department of Economics, Iowa State University.
  260 Heady Hall, Ames, IA 50011.
  Bartalotti: \protect\url{bartalot@iastate.edu};
  Calhoun: \protect\url{gcalhoun@iastate.edu} and
  \protect\url{http://gray.clhn.org};
  He: \protect\url{yanghe@iastate.edu}.}}

\begin{document}
\maketitle

First, we thank the reviewer for providing detailed and helpful comments, which we feel have significantly improved the quality of the draft.  Below we provide replies to the reviewer’s specific comments detailing how we address each comment.

\section{General overview of changes}

For this version of the paper, we have changed the bootstrap method from the
residual bootstrap to the wild bootstrap. We have also updated the simulations
to include DGPs featuring heteroskedasticity. We believe that the residual
bootstrap used in the previous version is theoretically correct even under
heteroskedastcity as long as the conditional variance is assumed to be smooth in
a neighorbood around the cutoff point, since the residual bootstrap we initially
proposed only resampled from that neighborhood, but we agree that in practice
the wild bootstrap is likely to be more accurate and can accomodate forms of
conditional heteroskedasticity that the residual bootstrap can not.

We have also relaxed the ``uniform kernel'' requirement and allow other kernels
that are popular in practice. The title of the paper has been updated to reflect
that change.

### 2016-08-09 main_paper.tex
Minor edit in Proof 1
In Algorithm 1, zero is in the RHS. In this proof, zero is in the LHS.
This commit makes them consistent with each other: zero in the RHS.
Minor typo on theorem 1
Delete reference to naive bootstrap in the first paragraph of Section 4.

\begin{theorem}\label{T1}
  Under Assumptions~\ref{A1} and~\ref{A2},
\begin{equation}
  \label{eq:4}
  \frac{(\hat\tau(h) - \Delta^{*}(h,b) - \tau)}{ V'(h, b)^{1/2}}
  \to^{d} N(0,1),
\end{equation}
where $\Delta^*(h,b)$ is defined by Equation~\ref{eq:9}.
\end{theorem}

@@

\section{Simulation Evidence}\label{sim}

This section presents evidence from Monte Carlo simulations that the bootstrap
procedures proposed in Section~\ref{boot} produce valid, robust confidence
intervals similar to those obtained by the analytical procedures established
in CCT. The bootstrap CIs obtained compare favorably to the analytical
alternative, with coverage slightly closer to nominal coverage and shorter
length of the intervals in the specifications implemented. We also find that
all of the bias corrected methods can offer substantial improvements over
estimators that do not bias correct, including a ``naive'' bootstrap procedure.

@@

\subsection{Proof of Theorem~\ref{T1}}
We have
\begin{equation*}
  \hat\tau(h) - \Delta^*(h,b) - \tau = (\hat\tau(h) - \E \hat \tau(h)) +
  (\E \hat \tau(h) - \tau) - (\E^* \hat \tau^*(h) - \tau^*).
\end{equation*}
By construction,
\begin{equation*}
  Y_i^* =
  \begin{cases}
    r_2(X_i/b)'H_2(b) \beta_{+,2}^* + \varepsilon_i^* & X_i > 0 \\
    r_2(X_i/b)'H_2(b) \beta_{-,2}^* + \varepsilon_i^* & X_i \leq 0
  \end{cases}
\end{equation*}
which, along with the definitions at the beginning of the appendix,
ensures that
\begin{align*}
  \E^* \hat\mu_{\bullet,1}^*(h) - \mu_{\bullet}^{*}
  = h^{2} \mu_{\bullet}^{*(2)} \Bf_{\bullet}(h)/2
\end{align*}
almost surely and, consequently,
\begin{equation*}
  \E^* \hat\tau^*(h) - \tau^{*} = h^2\, \mu_+^{*(2)} \Bf_+(h)/2
  - h^2\, \mu_{-}^{*(2)} \Bf_{-}(h)/2.
\end{equation*}
CCT's Lemma A1 implies that
\begin{equation*}
  \E \hat\tau(h) - \tau = h^2\, \mu_+^{(2)} \Bf_+(h)/2
  - h^2\, \mu_{-}^{(2)} \Bf_{-}(h)/2 + O_p(h^3)
\end{equation*}
as well, giving
\begin{align}
  \hat\tau(h) - & \E \hat\tau(h) + (\E \hat\tau(h) - \tau) - (\E^* \hat\tau^*(h) - \tau^*)\notag \\
  &= \hat\tau(h) - \E\hat\tau(h)
   + h^2 \big((\mu_{-}^{*(2)} - \mu_{-}^{(2)}) \Bf_{-}(h) /2
   - (\mu_+^{*(2)}-\mu_+^{(2)}) \Bf_{+}(h) / 2 \big) + O_p(h^{3}) \notag \\
  \label{eq:6}
  &= \hat\tau(h) - \E\hat\tau(h)
   + h^2 (\hat\mu_{-,2}^{(2)}(b) - \mu_-^{(2)}) \Bf_{-}(h) /2 \\
  \notag
  &\pushright{- h^2 (\hat\mu_{+,2}^{(2)}(b) - \mu_+^{(2)}) \Bf_{+}(h) / 2
   + O_p(h^{3})}
\end{align}
The second equality holds because
$\mu_\bullet^{*(2)} = \hat\mu_{\bullet,2}^{(2)}(b)$ almost surely. Asymptotic
normality then follows from normality of $\hat\tau(h) - \E\hat\tau(h)$ and
$\hat\mu_{\bullet,2}^{(2)}(b) - \mu_\bullet^{(2)}$ using similar arguments to
CCT's Lemma SA4.D.\qed

>>>>

\begin{theorem}\label{T1}
  Under Assumptions~\ref{A1} and~\ref{A2},
\begin{equation}
  \label{eq:4}
  \frac{(\hat\tau(h) - \Delta^{*}(h,b) - \tau)}{ V'(h, b)^{1/2}}
  \to^{d} N(0,1),
\end{equation}
where $\Delta^*(h,b)$ is defined by Equation~\eqref{eq:9}.
\end{theorem}

@@

\section{Simulation Evidence}\label{sim}
This section presents evidence from Monte Carlo simulations that the bootstrap
procedures proposed in Section~\ref{boot} produce valid, robust confidence
intervals similar to those obtained by the analytical procedures established
in CCT. The bootstrap CIs obtained compare favorably to the analytical
alternative, with coverage slightly closer to nominal coverage and shorter
length of the intervals in the specifications implemented. We also find that
all of the bias corrected methods can offer substantial improvements over
estimators that do not bias correct.

@@

\subsection{Proof of Theorem~\ref{T1}}
We have
\begin{equation*}
  \hat\tau(h) - \Delta^*(h,b) - \tau = (\hat\tau(h) - \E \hat \tau(h)) +
  (\E \hat \tau(h) - \tau) - (\E^* \hat \tau^*(h) - \tau^*).
\end{equation*}
By construction,
\begin{equation*}
  Y_i^* =
  \begin{cases}
    r_2(X_i/b)'H_2(b) \beta_{+,2}^* + \varepsilon_i^* & X_i \geq 0 \\
    r_2(X_i/b)'H_2(b) \beta_{-,2}^* + \varepsilon_i^* & X_i < 0
  \end{cases}
\end{equation*}
which, along with the definitions at the beginning of the appendix,
ensures that
\begin{align*}
  \E^* \hat\mu_{\bullet,1}^*(h) - \mu_{\bullet}^{*}
  = h^{2} \mu_{\bullet}^{*(2)} \Bf_{\bullet}(h)/2
\end{align*}
almost surely and, consequently,
\begin{equation*}
  \E^* \hat\tau^*(h) - \tau^{*} = h^2\, \mu_+^{*(2)} \Bf_+(h)/2
  - h^2\, \mu_{-}^{*(2)} \Bf_{-}(h)/2.
\end{equation*}
CCT's Lemma A1 implies that
\begin{equation*}
  \E \hat\tau(h) - \tau = h^2\, \mu_+^{(2)} \Bf_+(h)/2
  - h^2\, \mu_{-}^{(2)} \Bf_{-}(h)/2 + O_p(h^3)
\end{equation*}
as well, giving
\begin{align}
  \hat\tau(h) - & \E \hat\tau(h) + (\E \hat\tau(h) - \tau) - (\E^* \hat\tau^*(h) - \tau^*)\notag \\
  &= \hat\tau(h) - \E\hat\tau(h)
   + h^2 \big((\mu_{-}^{*(2)} - \mu_{-}^{(2)}) \Bf_{-}(h) /2
   - (\mu_+^{*(2)}-\mu_+^{(2)}) \Bf_{+}(h) / 2 \big) + O_p(h^{3}) \notag \\
  \label{eq:6}
  &= \hat\tau(h) - \E\hat\tau(h)
   + h^2 (\hat\mu_{-,2}^{(2)}(b) - \mu_-^{(2)}) \Bf_{-}(h) /2 \\
  \notag
  &\pushright{- h^2 (\hat\mu_{+,2}^{(2)}(b) - \mu_+^{(2)}) \Bf_{+}(h) / 2
   + O_p(h^{3})}
\end{align}
The second equality holds because
$\mu_\bullet^{*(2)} = \hat\mu_{\bullet,2}^{(2)}(b)$ almost surely. Asymptotic
normality then follows from normality of $\hat\tau(h) - \E\hat\tau(h)$ and
$\hat\mu_{\bullet,2}^{(2)}(b) - \mu_\bullet^{(2)}$ using similar arguments to
CCT's Lemma SA4.D.\qed
